---
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
#Load the packages required for this 
library(tidyverse)
library(leaflet)#package to make interactive web
library(leaflet.providers)#allows you to add third party basemaps
library(here)
library(plotly)
library(htmltools)
```

# Environmental data from aquaculture

Data collected from aquaculture locations throughout Washington. Data displayed here has not been quality controlled. Demonstration website.

## Map of sites

Click each location on this map to find a list of the data that has been collected at each site and the organisation that has collected this data. Can easily add more sites by adding rows to a CSV file.

```{r, echo = FALSE, results = "hide", include=FALSE}
###Create the map
#Read in site info
siteinfo <- read.csv(here("Site_info.csv"))
#Create the map - in the future set all of the variables in a csv to be read in 
aquaculturemap <- leaflet() %>% 
  addProviderTiles(providers$Esri.OceanBasemap) %>% 
  addMarkers(lng = siteinfo$Long, lat = siteinfo$Lat,
             popup = lapply(seq(nrow(siteinfo)), function(i) {
               HTML(paste0("<strong>", siteinfo$Site_name[i], "</strong><br>",
                           "Availble data: ", siteinfo$Data[i], "<br>",
                           "Organisation: ", siteinfo$Organisation[i], "<br>",
                           "Contact: ", siteinfo$Contact[i]))
             }))

```

```{r, echo = FALSE}
aquaculturemap
```

## Comparison of data across sites

### Disolved oxygen

```{r, include=FALSE}
#Create averages
##read in the data 
allthorndat <- read.csv(here("Data","thorn_Do_Temp.csv"))
allcheldat <- read.csv(here("Data","chelsea_Do_Temp.csv"))
allhooddat <- read.csv(here("Data","hood_Do_Temp.csv"))
allmandat <- read.csv(here("Data","man_Do_Temp.csv"))


#Set the first column as date
allthorndat$datetime <- mdy_hm(allthorndat$Date.Time..GMT.07.00)
allcheldat$datetime  <- mdy_hm(allcheldat$Date.Time..GMT.07.00)
allhooddat$datetime  <- mdy_hm(allhooddat$Date.Time..GMT.07.00)
allmandat$datetime  <- mdy_hm(allmandat$Date.Time..GMT.07.00)
#add a site columin to each of the DFs
allcheldat <- allcheldat %>% mutate(Site = "Chelsea")
allthorndat <- allthorndat %>% mutate(Site = "Thorndyke")
allhooddat <- allhooddat %>% mutate(Site = "Hood_Head")
allmandat <- allmandat %>% mutate(Site = "Manchester")
#add a date column to the two dfs
allcheldat$date <- as.Date(allcheldat$datetime)
allthorndat$date <- as.Date(allthorndat$datetime)
allhooddat$date <- as.Date(allhooddat$datetime)
allmandat$date <- as.Date(allmandat$datetime)
#calculate averages
chelav <- allcheldat %>% group_by(date) %>% summarise(meantemp=mean(Temp_C, na.rm = TRUE), meanDO=mean(DO_mgL, na.rm = TRUE))
thornav <- allthorndat %>% group_by(date) %>% summarise(meantemp=mean(Temp_C, na.rm = TRUE), meanDO=mean(DO_mgL, na.rm = TRUE))
manav <- allmandat %>% group_by(date) %>% summarise(meantemp=mean(Temp_C, na.rm = TRUE), meanDO=mean(DO_mgL, na.rm = TRUE))
hoodav <- allhooddat %>% group_by(date) %>% summarise(meantemp=mean(Temp_C, na.rm = TRUE), meanDO=mean(DO_mgL, na.rm = TRUE))
#Only caclulate the days I want
chelav <- chelav %>% filter(date > "2023-06-05")
thornav <- thornav %>% filter(date > "2023-06-05")
hoodav <- hoodav %>% filter(date > "2023-06-05")
manav <- manav %>% filter(date > "2023-06-05")
#calculate cumulative degree days
chelav$degdays <- cumsum(chelav$meantemp)
thornav$degdays <- cumsum(thornav$meantemp)
#Add site to the average dfs
chelav <- chelav %>% mutate(Site = "Chelsea")
thornav <- thornav %>% mutate(Site = "Thorndyke")
manlav <- manav %>% mutate(Site = "Manchester")
hoodav <- hoodav %>% mutate(Site = "Hood_Head")
#merge the two sites temperature data to plot
alldat <- bind_rows(allcheldat, allthorndat, allmandat, allhooddat)
allavdat <- bind_rows(chelav, thornav, hoodav, manav)
dailyaverages <- alldat
alldat$date <- as.Date(alldat$datetime) 
averagetemps <- alldat %>% group_by(date, Site) %>% summarise(meantemp=mean(Temp_C, na.rm = TRUE))
averageDO <- alldat %>% group_by(date, Site) %>% summarise(meanDO=mean(DO_mgL, na.rm = TRUE))

#Plot DO
avergage_DO_plot <- averageDO %>% 
  filter(date > "2023-06-05") %>% #filter(date < "2023-10-17") %>% 
  ggplot(aes(x= date , y = meanDO, colour = Site)) + geom_line()+
  theme_bw()+ylab("Daily Mean Dissolved Oxygen (mg / L)")+xlab("Date")+
  scale_color_manual(values=c("#B3C863","#756A8C","#037D64","#CEB08E"))+
  theme(axis.title.y=element_text())+
  theme(
    text = element_text(size = 14))

```

```{r, echo=FALSE}
ggplotly(avergage_DO_plot)
```

### Temperature
Note that these daily averages include time that individuals were out of the water at low tide sites.

```{r, include = FALSE}
averagetemps <- averagetemps %>% 
  filter(date > "2023-06-05") %>% #filter(date < "2023-10-17") %>% 
           ggplot(aes(x= date , y = meantemp, colour = Site)) + geom_line()+
  theme_bw()+ylab("Daily Mean Temperature (°C)")+xlab("Date")+
  scale_color_manual(values=c("#B3C863","#756A8C","#037D64","#CEB08E"))+
  theme(text=element_text(),
        axis.title.y=element_text())
```

```{r, echo=FALSE}
ggplotly(averagetemps)
```

Github page created by Craig Norrie. Last updated 2 July 2024. This could be a location to have data hosted from multiple projects. 