---
title: "Clam Bay environmental data"
format: html
editor: source
---





```{r, include=FALSE}
#Load the packages required to make a local scale map
library(tidyverse)
library(leaflet)#package to make interactive web
library(leaflet.providers)#allows you to add third party basemaps
library(here)
library(plotly)
library(lubridate)
```

## Site information

```{r, echo=FALSE, results='hide'}
aquaculturemap_man <- leaflet() %>% 
  addProviderTiles(providers$Esri.OceanBasemap) %>%
  addMarkers(lng = -122.545044,lat = 47.573528, popup = "Clam Bay - NOAA Manchester")
```

```{r, echo=FALSE}
aquaculturemap_man
```

<Br>Raw data can be found [here](https://github.com/CraigNorrie/Environmental-data-website/tree/main/Data)<Br>

```{r, echo=FALSE, results='hide'}
#Sumarise the data
#turn this into a loop that will do this for each of the cvs files that I have in the data folder
mandat <- read.csv(here("Data", "man_Do_Temp.csv"))#Read in the data
mandat$datetime <- mdy_hm(mandat$Date.Time..GMT.07.00)
#Obtain daily mean data - this should probably be done in a seperate script and this should be saved for the website only
manav <- mandat %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d")) %>%
  group_by(date) %>%
  summarise(meantemp = mean(Temp_C, na.rm = TRUE),
            meanDO = mean(DO_mgL, na.rm = TRUE))
```


## Temperature data

Temperature data was collected from hobo DO and temp logger.  Data was collected every 15 minutes and daily averages were calculated. Note this data included information from when individuals were out of the water. <Br>

```{r, echo=FALSE, results='hide'}
man_temp_plot <- manav %>% 
  ggplot(aes(x = date, y = meantemp))+geom_line()+xlab("Date")+ylab("Temperature (°C)")+theme_bw()

```

```{r, echo = FALSE}
ggplotly(man_temp_plot)
```

## Disolved oxygen data

Dissolved oxygen data was collected using a [HOBO dissolved oxygen data logger](https://www.onsetcomp.com/products/data-loggers/u26-001). Data was collected every 15 minutes and daily averages were calculated. 

```{r, echo=FALSE, results='hide'}
man_do_plot <- manav %>% 
  ggplot(aes(x = date, y = meanDO))+geom_line()+xlab("Date")+ylab("Disolved oxygen (mg/L)")+theme_bw()

ggplotly(man_do_plot)

```

```{r, echo = FALSE}
ggplotly(man_do_plot)
```

## Carbonate Chemistry

Samples were taken monthly and preserved with the addition of 200 µl of mercuric chloride. pH was determined spectrophotometrically using an ocean insights spectrophotometer. Total alkalinity was determind through volumetric titrations and the remainder of the carbonate system was paramaterised using [Seacarb in R](https://github.com/cran/seacarb).


```{r}
carbchem %>% filter(Site == "Manchester") %>% select(-c(1,2)) %>%  arrange(Year, Month)
```

